### 2022-05-24 project_Luis/paper.tex
luis
pictures changed

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}
    \vspace{\baselineskip}   
    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{./lumint.png}
  \caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
  \label{figure6}
\end{figure}

 \begin{figure}[H]
   \centering
   \includegraphics[width=0.7\columnwidth]{./pg.png}
   \includegraphics[width=0.29\columnwidth]{./higgs_couplings.png}
   \caption{
     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc-corr}.
   }
   \label{figureKappasUncs}
 \end{figure}

@@

~\ref{fig:CMS}.

@@

@@

\item {\bf Semester 2021-2}:
  \SubItem{ Course I: on particle physics, particle detection, or data analysis}
  \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
  \SubItem{ Analysis of the LHC Run 2 luminosity data using the PCC method}

\item {\bf Semester 2022-1}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
  \SubItem{ Completion of the analysis of the LHC Run 2 luminosity data using the PCC method}
  \SubItem{ Presentation of results at national or international conference}
  \SubItem{ Thesis writing}

>>>>

  \vspace{1cm}
  {
    TITLE:\par
    {\bf \large \ProjectTitle  \par}

    \vspace{0.4cm}
    TITULO:\par
    {\bf \large \ProjectTitleESP \par}
  }

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{./HL-LHC_2022.pdf}
  \caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
  \label{figure6}
\end{figure}

 \begin{figure}[H]
   \centering
   \includegraphics[width=0.6\columnwidth]{./pg.png}
   \includegraphics[width=0.39\columnwidth]{./Higgs-cross-sections-for-several-production-channels.png}
   \caption{
     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
     Right: Higgs boson cross sections for several production channels versus the LHC centre of mass energy  \cite{Cepeda:2019klc-corr}.
   }
   \label{figureKappasUncs}
 \end{figure}

@@

%~\ref{fig:CMS}.

@@

\item Understand the CMS silicon pixel detector including the barrel and endcap sensors.

\item Study the stability and linearity of the sensors in the different layers or disks of the pixel detector and select the stable components.

\item Determine new methods for measurement of the stability and linearity of the system.

@@

\item {\bf Semester 2021-2}:
  \SubItem{ Course I: on particle physics, particle detection, or data analysis}
  \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
  \SubItem{ Analysis of the LHC Run 3 luminosity data using the PCC method}

\item {\bf Semester 2022-1}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
  \SubItem{ Completion of the analysis of the LHC Run 3 luminosity data using the PCC method}
  \SubItem{ Presentation of results at national or international conference}
  \SubItem{ Thesis writing}
